graphs

### 2022-04-02 inputs/data/datasheet_template.Rmd
updated datasheet and graphs

1. *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
	- TBD
2. *Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)? If so, please provide a link or other access point to the "raw" data.*
	- TBD
3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
	- TBD
4. *Any other comments?*
	- TBD

@@

1. *Has the dataset been used for any tasks already? If so, please provide a description.*
	- TBD
2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
	- TBD
3. *What (other) tasks could the dataset be used for?*
	- TBD
4. *Is there anything about the composition of the dataset or the way it was collected and preprocessed/cleaned/labeled that might impact future uses? For example, is there anything that a dataset consumer might need to know to avoid uses that could result in unfair treatment of individuals or groups (for example, stereotyping, quality of service issues) or other risks or harms (for example, legal risks, financial harms)? If so, please provide a description. Is there anything a dataset consumer could do to mitigate these risks or harms?*
	- TBD
5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
	- TBD
6. *Any other comments?*
	- TBD

@@

1. *Will the dataset be distributed to third parties outside of the entity (for example, company, institution, organization) on behalf of which the dataset was created? If so, please provide a description.*
	- TBD
2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
	- TBD
3. *When will the dataset be distributed?*
	- TBD
4. *Will the dataset be distributed under a copyright or other intellectual property (IP) license, and/or under applicable terms of use (ToU)? If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
	- TBD
5. *Have any third parties imposed IP-based or other restrictions on the data associated with the instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
	- TBD
6. *Do any export controls or other regulatory restrictions apply to the dataset or to individual instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
	- TBD
7. *Any other comments?*
	- TBD

@@

1. *Who will be supporting/hosting/maintaining the dataset?*
	- TBD
2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
	- TBD
3. *Is there an erratum? If so, please provide a link or other access point.*
	- TBD
4. *Will the dataset be updated (for example, to correct labeling errors, add new instances, delete instances)? If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
	- TBD
5. *If the dataset relates to people, are there applicable limits on the retention of the data associated with the instances (for example, were the individuals in question told that their data would be retained for a fixed period of time and then deleted)? If so, please describe these limits and explain how they will be enforced.*
	- TBD
6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
	- TBD
7. *If others want to extend/augment/build on/contribute to the dataset, is there a mechanism for them to do so? If so, please provide a description. Will these contributions be validated/verified? If so, please describe how. If not, why not? Is there a process for communicating/distributing these contributions to dataset consumers? If so, please provide a description.*
	- TBD
8. *Any other comments?*
	- TBD

>>>>

1. *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
	- The data was originally obtained in PDF format. The table from the survey PDF was converted to a usable data frame in R using the library pdftools for R.
2. *Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)? If so, please provide a link or other access point to the "raw" data.*
	- The raw data obtained from the PDF is saved in inputs/data/raw_data.csv
3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
	- R Software is avalaible at https://www.R-project.org/
4. *Any other comments?*
	- The library used to help import data from PDF is available at https://docs.ropensci.org/pdftools/

@@

1. *Has the dataset been used for any tasks already? If so, please provide a description.*
	- The dataset has not been used for other tasks yet.
2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
	- https://github.com/haqbilal/India-1992-DHS-State-Findings
3. *What (other) tasks could the dataset be used for?*
	- The dataset can be used for examining the state of women and children in India in 1992-1993.
4. *Is there anything about the composition of the dataset or the way it was collected and preprocessed/cleaned/labeled that might impact future uses? For example, is there anything that a dataset consumer might need to know to avoid uses that could result in unfair treatment of individuals or groups (for example, stereotyping, quality of service issues) or other risks or harms (for example, legal risks, financial harms)? If so, please provide a description. Is there anything a dataset consumer could do to mitigate these risks or harms?*
	- The cleaning process is very specific to the way this table was formatted in the original PDF and may not work on other tables. 
5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
	- The dataset would not be appropriate for purposes other than examining the plight of women and children in 1992 India.

@@

1. *Will the dataset be distributed to third parties outside of the entity (for example, company, institution, organization) on behalf of which the dataset was created? If so, please provide a description.*
	- No, the dataset is openly available and being used for personal uses only.
2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
	- The dataset will be distributed using Github.
3. *When will the dataset be distributed?*
	- The dataset will be distributed in April 2022.
4. *Will the dataset be distributed under a copyright or other intellectual property (IP) license, and/or under applicable terms of use (ToU)? If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
	- The dataset will be released under the MIT license
5. *Have any third parties imposed IP-based or other restrictions on the data associated with the instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
	- There are no restrictions
6. *Do any export controls or other regulatory restrictions apply to the dataset or to individual instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
	- No such controls or restrictions are applicable.
7. *Any other comments?*

@@

1. *Who will be supporting/hosting/maintaining the dataset?*
	- Bilal Haq and Ritvik Puri
2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
	- Can be contacted via email at bilalhaq1219@gmail.com
3. *Is there an erratum? If so, please provide a link or other access point.*
	- There is no erratum available currently.
4. *Will the dataset be updated (for example, to correct labeling errors, add new instances, delete instances)? If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
	- Currently there is no plan of updating the dataset. If there are updates in the future, it will be done through Github.
5. *If the dataset relates to people, are there applicable limits on the retention of the data associated with the instances (for example, were the individuals in question told that their data would be retained for a fixed period of time and then deleted)? If so, please describe these limits and explain how they will be enforced.*
	- The dataset was made via survey findings conducted in India. There are no applicable limits as the people took part voluntarily.
6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
	- The older versions would not be hosted. Dataset consumers will be able to check whether the dataset has been updated through Github commit history.
7. *If others want to extend/augment/build on/contribute to the dataset, is there a mechanism for them to do so? If so, please provide a description. Will these contributions be validated/verified? If so, please describe how. If not, why not? Is there a process for communicating/distributing these contributions to dataset consumers? If so, please provide a description.*
	- There is no mechanism for accepting contribtuions from other users as of now.

### 2022-04-02 outputs/graphs.Rmd
updated datasheet and graphs

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(DiagrammeR)
library(reshape2)
library(here)
library(knitr)

@@

Graphs
```{r}
# Illiterate females get married early
dhs %>%
  ggplot(aes(`Percent of illiterate females`, `Percent of women married before age 18`, color = states)) +
  geom_point()

@@

# Women going to school in each state
dhs %>%
  ggplot(aes(x=states, y=`Percent of females attending schools`)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  theme_bw()
  #theme(axis.text.x = element_text(angle = 90))

@@

```{r}
#States with household toilet & water pipes
nigib1 <- data.frame(dhs$states, dhs$`Percent of households with drinking water from pipe`, dhs$`Percent of households with no toilet facility`)
colnames(nigib1) <- c("States", "Water", "Toilets")
nigib2 <- reshape2::melt(nigib1, id.vars = 'States')

@@

```{r}
# Per state, underwight stunted and wasted children
nigib1 <- data.frame(dhs$states, dhs$`Percent of children underweight`, dhs$`Percent of children stunted`, dhs$`Percent of children wasted`)
colnames(nigib1) <- c("States", "Underwight", "Stunted", "Wasted")
nigib2 <- reshape2::melt(nigib1, id.vars = 'States')

@@

```{r}
tiny_dhs <- dhs |>
  select(c(1, 2, 4, 14, 16, 19))
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(DiagrammeR)
library(reshape2)
library(here)
library(knitr)
library(patchwork)

@@

Graphs
```{r}
# Illiterate females get married early
dhs %>%
  ggplot(aes(`Percent of illiterate females`, `Percent of women married before age 18`, color = States)) +
  geom_point()

@@

# Women going to school in each state
dhs %>%
  ggplot(aes(x=States, y=`Percent of females attending schools`)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  theme_bw()
  #theme(axis.text.x = element_text(angle = 90))

@@

```{r}
#States with household toilet & water pipes
nigib1 <- data.frame(dhs$States, dhs$`Percent of households with drinking water from pipe`, dhs$`Percent of households with no toilet facility`)
colnames(nigib1) <- c("States", "Water", "Toilets")
nigib2 <- reshape2::melt(nigib1, id.vars = 'States')

@@

```{r}
# Per state, underwight stunted and wasted children
nigib1 <- data.frame(dhs$States, dhs$`Percent of children underweight`, dhs$`Percent of children stunted`, dhs$`Percent of children wasted`)
colnames(nigib1) <- c("States", "Underwight", "Stunted", "Wasted")
nigib2 <- reshape2::melt(nigib1, id.vars = 'States')

@@

```{r}
tiny_dhs <- dhs %>%
  select(c(1, 2, 4, 14, 16, 19))
```

```{r}
kable(head(tiny_dhs, 5))
```

```{r}
tiny_dhs %>%
  ggplot(aes(`Percent of illiterate females`, `Percent of children fully immunized`)) +
  geom_point() +
  geom_smooth(method='lm')
```

```{r}
tiny_dhs %>%
  ggplot(aes(`Percent of mothers receiving antenatal care`, `Percent of births delivered in health facility`)) +
  geom_point() +
  geom_smooth(method='lm')
```

```{r}
tiny_dhs %>%
  ggplot(aes(`Percent of illiterate females`, `Percent of births delivered in health facility`)) +
  geom_point() +
  geom_smooth(method='lm')
```

```{r}
tiny_dhs <- tiny_dhs %>%
  mutate(illiterate = case_when(
    `Percent of illiterate females` >= 56.7 ~ 1,
    `Percent of illiterate females` < 56.7 ~ -1
  ))

tiny_dhs <- tiny_dhs %>%
  mutate(antenatal = case_when(
    `Percent of mothers receiving antenatal care` >= 62.3 ~ 1,
    `Percent of mothers receiving antenatal care` < 62.3 ~ -1
  ))

tiny_dhs <- tiny_dhs %>%
  mutate(water = case_when(
    `Percent of households with drinking water from pipe` >= 68.2 ~ 1,
    `Percent of households with drinking water from pipe` < 68.2 ~ -1
  ))

tiny_dhs <- tiny_dhs %>%
  mutate(births = case_when(
    `Percent of births delivered in health facility` >= 25.5 ~ 1,
    `Percent of births delivered in health facility` < 25.5 ~ -1
  ))

tiny_dhs <- tiny_dhs %>%
  mutate(immunized = case_when(
    `Percent of children fully immunized` >= 35.4 ~ 1,
    `Percent of children fully immunized` < 35.4 ~ -1
  ))
```

```{r}
ip1 <- interaction.plot(tiny_dhs$illiterate, tiny_dhs$antenatal, tiny_dhs$births)
ip2 <- interaction.plot(tiny_dhs$illiterate, tiny_dhs$antenatal, tiny_dhs$immunized)

ip3 <- interaction.plot(tiny_dhs$illiterate, tiny_dhs$water, tiny_dhs$births)
ip4 <- interaction.plot(tiny_dhs$illiterate, tiny_dhs$water, tiny_dhs$immunized)

ip5 <- interaction.plot(tiny_dhs$antenatal, tiny_dhs$water, tiny_dhs$births)
ip6 <- interaction.plot(tiny_dhs$antenatal, tiny_dhs$water, tiny_dhs$immunized)
```

```{r}
# Health facility v/s immunization
view(tiny_dhs)
nigib1 <- data.frame(tiny_dhs$States, tiny_dhs$`Percent of births delivered in health facility`, tiny_dhs$`Percent of children fully immunized`)
colnames(nigib1) <- c("States", "Health Facility", "Immunized")
nigib2 <- reshape2::melt(nigib1, id.vars = 'States')

nigib2 %>%
  ggplot(aes(x = States, y = value, fill=variable)) +
  geom_bar(stat = "identity", position = "dodge") +
  coord_flip()

#Illiterate females v/s antenatal care
nigib1 <- data.frame(tiny_dhs$States, tiny_dhs$`Percent of illiterate females`, tiny_dhs$`Percent of mothers receiving antenatal care`)
colnames(nigib1) <- c("States", "Illiterate Females", "Antenatal Care")
nigib2 <- reshape2::melt(nigib1, id.vars = 'States')
